The title

### 2017-11-02 article.tex
Removed bonus theorem about model instanciation
Moved example in appendix

\section{Example}
The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
A general model is a model that claims it satisfies the general conditions.

\section{Theorem}
\subsection{Main}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
\end{theorem}
\begin{proof}
Define $\wibeatse^\text{ext} \subseteq \allargs × \allargs$ as: $\ar' \wibeatse^\text{ext} \ar$ iff $\ar' \wibeatse \ar ∨ (\ar \in \mleadstoinv ∧ \ar' \ibeatse \ar)$.

@@

\subsection{Bonus}
A model $\eta' = (\mbeats', \mleadsto', +')$ particularizes a model $\eta = (\mbeats, \mleadsto, +)$ iff $\mbeats' = \mbeats, \mleadsto' \subseteq \mleadsto, +' = +$.
\begin{theorem}[Instanciation]
	Given a decision situation and a model $\eta$ and a model particularization $\eta'$, if $\eta$ satisfies the general conditions, then $\eta'$ satisfies the general conditions.
\end{theorem}

@@

\section{Example}
s2 argues in favor of p against s1: s "le monde n’est pas fiable". s1 "le monde est fiable, bhl l’a dit". s2 "bhl est un clown, il s’est planté sur l’Irak". s3 "il avait raison sur l’Irak : l’Irak a des ADM". s4 "l’Irak n’a pas d’ADM, Bush l’a reconnu".
Does s4 attack s3?
"bhl est un clown, il s’est planté sur l’irak" + "l’irak n’a pas d’ADM, Bush l’a reconnu" VS "il avait raison sur l’Irak : l’Irak a des ADM" !

>>>>

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$.
\end{theorem}
\begin{proof}
Define $\wibeatse^\text{ext} \subseteq \allargs × \allargs$ as: $\ar' \wibeatse^\text{ext} \ar$ iff $\ar' \wibeatse \ar ∨ (\ar \in \mleadstoinv ∧ \ar' \ibeatse \ar)$.

@@

@@

\section{Example about model instanciation}
The general conditions are Reinstatement, Justifiable unstability, Finite defense and Covering.
A general model is a model that claims it satisfies the general conditions.

\section{Example about default arguments}
s2 argues in favor of p against s1: s "le monde n’est pas fiable". s1 "le monde est fiable, bhl l’a dit". s2 "bhl est un clown, il s’est planté sur l’Irak". s3 "il avait raison sur l’Irak : l’Irak a des ADM". s4 "l’Irak n’a pas d’ADM, Bush l’a reconnu".
Does s4 attack s3?
"bhl est un clown, il s’est planté sur l’irak" + "l’irak n’a pas d’ADM, Bush l’a reconnu" VS "il avait raison sur l’Irak : l’Irak a des ADM" !
